Validate Structural Analysis \\ \large Testing GPV Method in First-Price Reverse Auctions

### 2020-12-06 paper/paper.tex
finish simulation section

\author{Qingbo Liu\\[0.5cm]{\small Advisor: Timothy P. Hubbard}}
\date{Nov 30, 2020}

@@

The differential equation characterizes the strategy in sealed-bid first-price 
reverse auction and the solution of it, $s(\cdot)$, gives the equilibrium 
bidding function as follows \cite{HubbardPaarsch2009}
\begin{equation}
    s(c) = b =  c + \frac{\int_c^{\overline{c}} [1 - F(u)] du}{[1 - F(c)]^{n-1}}
    \label{eqn:BiddingFunction}
\end{equation}

@@

\section[title]{Simulation 
\footnote{This paper is still a work in progress and I am investigating the 
reason why the result is so. For the latest version on this section, please 
see \url{https://github.com/QuRyu/CDOT/blob/main/paper/paper.pdf }} } 
To test if the estimated cost distribution captures the underlying cost 
distribution that drives observed bids, I will proceed to the second step 
of the adapted cross-validation: simulate bids using estimated cost distribution 
$F_c(\cdot)$ and comparing simulated bids to actual bids. For the test data, 
I will use an auction from the dataset which has 16 bidders. The data is not used 
to estimate the cost distribution because the total number of bids with 
$16$ bidders is less than $32$.

The simulation technique is known as the inversion method and runs as follows.
I will draw 16 random numbers uniformly 
distributed on the range $(0 ,1)$ and use the inverse distribution function, 
$F_c^{-1}(\cdot)$ to find the corresponding costs. The bids are then computed 
using equation (\ref{eqn:BiddingFunction}) and the estimated cost distribution 
$F_c$. This process is repeated 1000 times and the averages are taken.

\begin{table}
    \begin{tabular}{llllll}
    \hline
    Normalized Bids     & Mean                    & Median                   & \begin{tabular}[c]{@{}l@{}}Standard\\ Deviation\end{tabular} & Max                           & Min                          \\ \hline
    Test data           & 91.72\% & 73.11\%       & 0.355\%                  & 178.43\% & 58.74\% \\ \hline
    Simulated Bids      & $1.487 \cdot 10^{46}\%$   & $1.758 \cdot 10^{38}\%$    & $5.759 \cdot 10^{46}\%$                               & $2.230 \cdot 10^{47}\%$         & $7.811 \cdot 10^{32}\%$        \\ \hline
    \end{tabular}
    \caption{Summary Statisticals of test data and simulated dataset}
    \label{table:2}
\end{table}

Table \ref{table:2} summarizes the test data and simulated bids, respectively. The 
anomaly of the simulated data comes from the fact the 15th power of $1-F_c(c)$, a
number that is less than 1, is tiny and so $\frac{1}{1-F_c(c)}$ is large,
inflating the result by an astronomical magnitude.

>>>>

\author{Qingbo Liu\\[0.5cm]{\small Advisor: Timothy P. Hubbard}}

@@

The differential equation characterizes the strategy in sealed-bid first-price 
reverse auction and the solution of it, $s(\cdot)$, gives the equilibrium 
bidding function as follows \cite{HubbardPaarsch2009}
\begin{equation}
    s(c) = b =  c + \frac{\int_c^{\overline{c}} [1 - F(u)]^{n-1} du}{[1 - F(c)]^{n-1}}
    \label{eqn:BiddingFunction}
\end{equation}

@@

\section[title]{Simulation 
\footnote{This paper is still a work in progress and I am investigating the 
reason why the result is so. For the latest version on this section, please 
see \url{https://github.com/QuRyu/CDOT/blob/main/paper/paper.pdf }} } 
To test if the estimated cost distribution captures the underlying cost 
distribution that induces observed bids, I will proceed to validation stage: 
simulate bids using estimated cost distribution 
$F_c(\cdot)$ and comparing simulated bids to actual bids. For the test data, 
I will use an auction from the dataset which has 16 bidders. The data is not used 
to estimate the cost distribution because the total number of bids with 
$16$ bidders is less than $32$.

The simulation technique is known as the inversion method and runs as follows.
I will draw 16 random numbers uniformly 
distributed on the range $(0 ,1)$ and use the inverse distribution function, 
$F_c^{-1}(\cdot)$, to find the corresponding costs. The bids are then computed 
using equation (\ref{eqn:BiddingFunction}) and the estimated cost distribution 
$F_c$. This process is repeated 1000 times and the averages are taken.

\begin{figure}
\centering 
    \begin{minipage}[h]{0.55\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{simulated_bids.jpg}
        \caption{Simulated bids against simulated costs.}
        \label{fig:simulation}
    \end{minipage}%
    \begin{minipage}[h]{0.55\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{actualVsimulated.jpg}
        \caption{Bids from test data (x-axis) plotted 
        against simulated bids (y-axis).}
        \label{fig:actualVsimulation}
    \end{minipage}
\end{figure}

Figure \ref{fig:simulation} plos simulated costs against simulated bids that are 
inferred from simulated costs using equation (\ref{eqn:BiddingFunction}). 
The simulated costs and bids center around 110\% 
and the range is small, with the max and min differing by less than 4\%. This 
is due to the estimated unimodal cost distribution 
concentrating in the range [80, 200], with the peak around 110\%. 
With the inversion method repeated for 1000 times, it is natural that 
the costs and bids fall into the place where most bids and costs are 
concentrated. With the number of runs curtailed to 100 and 50, as shown in 
Figure \ref{fig:simulation_run_times}, the bids become more spread out and 
closer to the bid distribution. This shows that the number of runs is 
an important factor to determine in roder to have a more accurate simulation 
but it is outside the scope of this paper. For simplicity, I will keep 
referencing the data generated with 1000 runs.

\begin{figure}
\centering
    \begin{minipage}[h]{0.5\textwidth}
        \centering 
        \includegraphics[width=\linewidth]{100run.jpg}
    \end{minipage}%
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=\linewidth]{10run.jpg}
    \end{minipage}
\caption{Bid simulation run for 100 times (left) and 10 times(right)}
\label{fig:simulation_run_times}
\end{figure}

Figure \ref{fig:actualVsimulation} plots test data against simulated bids. 
A wide difference between simulation and test data is observed here. 
This difference, however, is not unexpected for two reasons: 
(1) the test data, which contains an auciton with 16 bidders, does not conform 
to the the bid distribution depicted in Figure \ref{fig:BidFrequency}, and 
(2) I am comparing most likely bids predicted by the estimated cost distribution 
to a particular auction. Therefore, the difference here not suggest the 
inaccuracy of the estimated cost distribution or the equilibrium model. 
Instead, this exercise suggests that we may need to increase the sample size 
to have a more informative comparison.
